\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,booktabs,array,hyperref,xcolor}
\usepackage{algorithm}
\usepackage[compatible]{algpseudocode}
\usepackage{listings}
\usepackage{enumitem}
\hypersetup{colorlinks=true,urlcolor=blue,citecolor=blue,linkcolor=blue}
\lstset{basicstyle=\ttfamily\small,breaklines=true,columns=fullflexible,frame=single}

\title{Supplementary Material: Reproducibility, Prompt Design, Trustworthiness, and Extended Evaluation for LAMI}
\author{Nishat Mahdiya Khan, Pronaya Bhattacharya, Qiyang Zhang, Praveen Kumar Donta, Thippa Reddy Gadekallu}
\date{}

\begin{document}
\maketitle

\section{Purpose and Scope}
This supplementary material supports the manuscript ``Agentic Metasurface Intelligence for IRS in 6G Edge Networks.'' The main article is constrained by the IEEE Communications Magazine page limit and therefore retains only the essential system description, evaluation summary, and practical limitations. This document provides additional reproducibility material: semantic input-output formats, prompt templates, closed-loop pseudocode, mathematical model, trustworthiness checks, fine-tuning assumptions, latency/energy accounting, scalability analysis, and artifact organization.

No over-the-air IRS hardware experiment is claimed. The FPGA actuation stage is represented as bounded discrete control actions and the external knowledge/context module is simulated.

\section{System Model and IRS Control Vector}
Let $\mathcal{U}=\{1,\ldots,U\}$ denote the edge clients and let $N$ denote the number of IRS reflecting elements. The IRS phase vector at control interval $t$ is
\begin{equation}
\boldsymbol{\phi}_{t}=[\phi_{1,t},\ldots,\phi_{N,t}]^{T},\quad
\phi_{n,t}=\beta_{n,t}e^{j\theta_{n,t}},
\end{equation}
where $0\leq\beta_{n,t}\leq1$ and $\theta_{n,t}\in\mathcal{Q}_{B}$. The $B$-bit phase codebook is
\begin{equation}
\mathcal{Q}_{B}=\left\{0,\frac{2\pi}{2^B},\ldots,\frac{2\pi(2^B-1)}{2^B}\right\}.
\end{equation}
The main evaluation uses $N=64$ elements, while the scalability reconstruction considers $N\in\{64,128,256,512,1024\}$.

The effective cascaded channel for user $u$ is represented as
\begin{equation}
h^{\mathrm{eff}}_{u,t}=h_{d,u,t}+\mathbf{h}^{H}_{r,u,t}\mathrm{diag}(\boldsymbol{\phi}_{t})\mathbf{G}_{t},
\end{equation}
where $h_{d,u,t}$ is the direct link, $\mathbf{G}_{t}$ is the BS--IRS channel, and $\mathbf{h}_{r,u,t}$ is the IRS--user channel. The SNR is
\begin{equation}
\gamma_{u,t}=\frac{P_t|h^{\mathrm{eff}}_{u,t}|^2}{\sigma^2+I_{u,t}}.
\end{equation}
A compact control objective is
\begin{equation}
\max_{\boldsymbol{\phi}_{t}}\sum_{u\in\mathcal{U}}w_u\log_2(1+\gamma_{u,t})-\lambda_EE_t-\lambda_LL_t-\lambda_{\Delta}\|\boldsymbol{\phi}_{t}-\boldsymbol{\phi}_{t-1}\|_0.
\end{equation}
The final term penalizes unnecessary global IRS updates and motivates selective element/region reconfiguration.

\section{Semantic Input and Output Formats}
Each edge SLM observes a local vector
\begin{equation}
\mathbf{z}_{u,t}=[\gamma_{u,t},I_{u,t},E_{u,t},v_{u,t},q_{u,t},p_{u,t}],
\end{equation}
including SNR, interference, energy state, mobility indicator, queue/load, and priority.

\subsection{Semantic Input JSON}
\begin{lstlisting}[language=json]
{
  "client_id": "u_007",
  "timestamp": 128.40,
  "measured_snr_db": 16.8,
  "snr_trend": "decreasing",
  "interference_db": 5.0,
  "mobility_state": "medium",
  "energy_state": 0.71,
  "priority_level": 2,
  "intent_scores": {
    "coverage_recovery": 0.82,
    "interference_suppression": 0.64,
    "energy_saving": 0.31
  },
  "slm_confidence": 0.87,
  "region_hint": 4
}
\end{lstlisting}

\subsection{Bounded LLM Output JSON}
\begin{lstlisting}[language=json]
{
  "control_mode": "selective_update",
  "target_regions": [3, 4],
  "phase_delta_code": [0, 0, 0, 1, -1, 0, 0, 0],
  "confidence": 0.91,
  "fallback_required": false,
  "reason_code": "localized_interference_recovery"
}
\end{lstlisting}

\section{Closed-loop Agentic Workflow}
\begin{algorithm}[h]
\caption{Closed-loop LAMI reasoning and IRS actuation}
\begin{algorithmic}[1]
\State Initialize valid IRS phase vector $\boldsymbol{\theta}_0$ and memory buffer $\mathcal{M}_0$.
\For{each control interval $t$}
    \State Each edge SLM observes local state $\mathbf{z}_{u,t}$.
    \State Generate semantic descriptor $\mathbf{s}_{u,t}$ and confidence $c_{u,t}$.
    \State Aggregate descriptors using confidence-priority weighting.
    \State Retrieve bounded memory $\mathcal{M}_{t-K:t-1}$.
    \State Generate candidate control action $\hat{a}_t$ as bounded JSON.
    \State Validate $\hat{a}_t$ using schema, phase, sparsity, confidence, and passivity checks.
    \If{validation passes}
        \State Apply IRS update through the control abstraction.
    \Else
        \State Apply fallback controller: hold state, cached-safe profile, or conventional codebook.
    \EndIf
    \State Observe post-actuation SNR, latency, and energy; update memory.
\EndFor
\end{algorithmic}
\end{algorithm}

The bounded memory is
\begin{equation}
\mathcal{M}_{t}=\{(\mathbf{S}_{\tau},\boldsymbol{\theta}_{\tau},\gamma_{\tau},L_{\tau},E_{\tau},\eta_{\tau})\}_{\tau=t-K}^{t-1}.
\end{equation}

\section{Trustworthiness and Safety Checks}
The system uses a four-stage safety envelope. First, low-confidence SLM descriptors are down-weighted. Second, conflicting semantic inputs are aggregated through normalized confidence-priority weights:
\begin{equation}
\alpha_{u,t}=\frac{c_{u,t}p_{u,t}}{\sum_{v\in\mathcal{U}}c_{v,t}p_{v,t}}.
\end{equation}
Third, LLM outputs are accepted only when confidence exceeds $\tau_{\mathrm{LLM}}$. Fourth, the physical validator enforces
\begin{equation}
\theta_{n,t}\in\mathcal{Q}_{B},\quad 0\leq\beta_{n,t}\leq1,\quad \|\boldsymbol{\theta}_{t}-\boldsymbol{\theta}_{t-1}\|_0\leq\Delta_{\max}.
\end{equation}
Invalid or uncertain actions trigger fallback control.

\section{Latency and Energy Accounting}
The complete control-path latency can be decomposed as
\begin{equation}
T_{\mathrm{total}}=T_{\mathrm{SLM}}+T_{\mathrm{uplink}}+T_{\mathrm{fusion}}+T_{\mathrm{LLM}}+T_{\mathrm{validation}}+T_{\mathrm{FPGA}}.
\end{equation}
The reported controller-side reasoning latency excludes full OTA propagation, sensing-chain delay, and real IRS bias-network settling time unless explicitly included in full-path accounting. Energy per decision is computed as
\begin{equation}
E_{\mathrm{decision}}=\int_{t_0}^{t_1}\left(P_{\mathrm{active}}(t)-P_{\mathrm{idle}}\right)dt.
\end{equation}

\section{Simulation Parameters}
\begin{center}
\begin{tabular}{ll}
\toprule
Parameter & Value \\
\midrule
Carrier frequency & 6 GHz \\
Transmit power & 30 dBm \\
Noise floor & $-90$ dBm \\
Path-loss exponent & 2.4 \\
IRS elements & 64 \\
Element spacing & 2.5 cm \\
Channel model & Rician fading \\
Rician K-factor & 6 dB \\
IRS failure rate & 10--15\% \\
Interference burst & 5 dB for 100 ms \\
Distance range & 10--200 m \\
Default realizations in artifact & 100 \\
\bottomrule
\end{tabular}
\end{center}

\section{Artifact Repository}
The accompanying repository contains prompt files, JSON schemas, pseudocode, configuration files, and Python scripts for reconstructing SNR recovery, distance adaptation, latency/energy accounting, trustworthiness validation, and scalability trends.

\section{Limitations and Non-claims}
This supplementary package does not claim real IRS hardware, OTA testing, live external API use, or production FPGA implementation. It provides a transparent controller-side reconstruction of the methodology and evaluation trends under the stated assumptions. Real deployment requires IRS testbed validation, measured channel traces, hardware timing characterization, and regulatory-compliant edge deployment.

\end{document}
